\lettrine[nindent=0em,lines=3]{O}ur customer WantCloud BV wants to develop an application in which users can solve Sudoku puzzles.
One feature is the automatic completion of a partially filled in puzzle.
To lower the client side workload this computation is performed on a remote server, our task is to create this server side application.
The traditional approach is to buy server hardware and host the application on it.
However this is time consuming, expensive, and scaling demands extra effort.
Therefore such services are nowadays hosted on cloud computing services such as Infrastructure as a Service (IaaS) in which provides virtual machines that can be dynamically allocated.
So our problem can be defined as: how do we create a fast, reliable, elastic Sudoku solving application on an IaaS service?

Existing systems use platforms like Amazon EC2\cite{ec2}, Microsoft Azure\cite{azure} or Google Compute Engine\cite{google}.
Usually elasticity is provided through an API by which developers can measure workload and provision computational power.
There are also services that can do this automatically such as Amazon Elastic Load Balancing. 

Our solution to the problem described is \appName, a fast and reliable cloud based Sudoku solver running on Amazon EC2\cite{ec2}. 
\appName features one main server to which all request are made, and a variable number of solver machines over which the jobs are distributed.
\appName provides elasticity by automatically provisioning solver machine VM's according to workload, and is resistant to system failures of solver machines.

The remainder of this article is structured as follows.
Section 2 describes the background of the application and its requirements.
The system design including resource management architecture and system policies are presented in section 3.
In section 4 we evaluate the performance of our system in production. Section 5 summarizes our main findings and discusses tradeoffs in our design.
The 6$^{th}$ section concludes this paper. 
